### 2017-01-13 second-order-rdsa-gen.tex
sir corrections first intro only

The 2RDSA-IH algorithm obtains three function samples $y_n$, $y_n^+$ and $y_n^-$ at $\theta_n$, $\theta_n+\delta_n d_n$ and $\theta_n - \delta_n d_n$, respectively, i.e.,
$y_n = f(\theta_n) + \xi_n$, $y_n^+ = f(\theta_n+\delta_n d_n) + \xi_n^+$ and 
$y_n^- = f(\theta_n-\delta_n d_n) + \xi_n^-$,
where the noise terms $\xi_n, \xi_n^+, \xi_n^-$ satisfy $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n\right] = 0$ with $\F_n = \sigma(\theta_m,m\le n)$ denoting the underlying sigma-field.

\section{Generalised RDSA gradient estimate}
The RDSA estimate of the gradient $\nabla f(\theta_n)$ is given by
\begin{align}
\label{eq:grad-gen}
\widehat\nabla f(\theta_n) = \frac1{\lambda} d_n \left[ \dfrac{y_n^+ - y_n^-}{2\delta_n}\right],
\end{align}
where $\lambda = \E(d_n^i)^2 $ and the perturbations $d_n^i$, $i=1,\ldots,N$ are i.i.d and zero-mean random variables. 
%Note that $E d_n^i = 0$, $E (d_n^i)^2 = 1+\epsilon$ and $E (d_n^i)^4 = \dfrac{(1+\epsilon)(1+(1+\epsilon)^3)}{(2+\epsilon)}$.

>>>>

The generalised 2RDSA algorithm obtains three function samples $y_n$, $y_n^+$ and $y_n^-$ at $\theta_n$, $\theta_n+\delta_n d_n$ and $\theta_n - \delta_n d_n$, respectively, i.e.,
$y_n = f(\theta_n) + \xi_n$, $y_n^+ = f(\theta_n+\delta_n d_n) + \xi_n^+$ and 
$y_n^- = f(\theta_n-\delta_n d_n) + \xi_n^-$,
where the noise terms $\xi_n, \xi_n^+, \xi_n^-$ satisfy $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n\right] = 0$ with $\F_n = \sigma(\theta_m,m\le n)$ denoting the underlying sigma-field.

\section{Generalised RDSA gradient estimate}
The generalised RDSA estimate of the gradient $\nabla f(\theta_n)$ is given by
\begin{align}
\label{eq:grad-gen}
\widehat\nabla f(\theta_n) = \frac1{\lambda} d_n \left[ \dfrac{y_n^+ - y_n^-}{2\delta_n}\right],
\end{align}
where $\lambda = \E(d_n^i)^2 $ and the perturbations $d_n^i$, $i=1,\ldots,N$ are i.i.d and zero-mean random variables. 
%Note that $E d_n^i = 0$, $E (d_n^i)^2 = 1+\epsilon$ and $E (d_n^i)^4 = \dfrac{(1+\epsilon)(1+(1+\epsilon)^3)}{(2+\epsilon)}$.
